### 2017-12-05 submission/manuscript.Rmd
complete addition of tables to be used in mansucript

@@

>>>>

# Read in mock sample number of OTU results
mock_anova_summary <- read_csv("../data/process/tables/mock_overall_anova_results.csv")
mock_tukey_summary <- read_csv("../data/process/tables/mock_overall_tukey_results.csv")

@@

# Read in sequence error count results
kruskal_seq_error_count <- read_csv("../data/process/tables/mock_error_count_overall_kruskal_results.csv")
dunn_seq_error_count <- read_csv("../data/process/tables/mock_error_count_overall_dunn_results.csv")

# Read in chimera prevalence results
kruskal_chimera_prev <- read_csv("../data/process/tables/mock_chimera_overall_kruskal_results.csv")
dunn_chimera_prev <- read_csv("../data/process/tables/mock_chimera_overall_dunn_results.csv")
